---
title: Dashboard
format: dashboard
---

## Overview 

This dashboard analyzes whether California's proposed 2025 congressional map (Proposition 50) increases partisan advantage compared to the 2024 map.

## Key Metrics 

### Column

**2024 Efficiency Gap**

```{r}
round(eg_2024 * 100, 2)
```
### Column

**2025 Efficiency Gap**

```{r}
round(eg_2025 * 100, 2)
```
### Column

**Difference**

```{r}
round((eg_2025 - eg_2024) * 100, 2)
```
## Analysis

### Comparison Chart
```{r}
#| echo: false
tibble(
  Map = c("2024", "2025"),
  `Efficiency Gap (%)` = c(eg_2024 * 100, eg_2025 * 100)
) %>%
  ggplot(aes(x = Map, y = `Efficiency Gap (%)`)) +
  geom_col(fill = c("steelblue", "coral")) +
  geom_hline(yintercept = 7, linetype = "dashed", color = "red") +
  geom_hline(yintercept = -7, linetype = "dashed", color = "red") +
  labs(title = "Efficiency Gap Comparison",
       subtitle = "Red lines show ±7% threshold") +
  theme_minimal()
```

### Findings 

**Key Results:**

1. The 2024 map had an efficiency gap of [X]%
2. The 2025 map has an efficiency gap of [Y]%
3. This represents a [increase/decrease] of [Z] percentage points